Learning Useful Changes\\(to Reduce Runtimes and Software Defects)

### 2015-08-20 Manuscript.tex
Updates from ShareLaTeX

\title{Prediction is Hard (Especially About the Future)}
\numberofauthors{2} 
\author{
\alignauthor 
Rahul Krishna \\
       \affaddr{CS, NcState, USA}\\
       {i.m.ralk@gmail.com}
\alignauthor
Tim Menzies\\
       \affaddr{CS, NcState, USA}\\
       {tim.menzies@gmail.com}}
\setlength{\columnsep}{7mm}

\maketitle
\begin{abstract}
 As business users demand more insightful
 analytics, data scientists need to change
 their tools. Instead of merely predicting 
 some result, they also need tools that generate ``plans'';
 i.e. specific suggestions on  how to change values in order to
 improve on some predicted value.

@@

 This paper uses these learners to learn methods
 to reduce defects and decrease program runtime.
 For the test data of this paper, those improvements   reduce
 the expected values of defect counts and  runtimes to    
 72\%,75\%  (median) and 66\%,20\% (best case) of the initial values, respectively.cy
\end{abstract}
\section{Introduction}
	How should we handle ``unpopulular'' results
	for data analytics? For example, if a business manager is presented
	with a data mining result that troubles them (e.g. an estimate of
	development time that is distressingly long), what advice
	can we offer them on management actions to {\em change} that estimate?

	This is an important question, and one with much currency in industry.
	In the summer of 2011 and 2012, one of us (Menzies) spent two months
	working on-site at Microsoft Redmond,
	observing data mining analysts.  He
	noted how Microsoft's data scientists
	discussed their data with  business users. 
	One surprising outcome of that study was just how
	little time was spent  
	inspecting  of the output of data miners as compared to another process, which we call {\em peeking}.
	In {\em peeking}, analysts and users spend much time
	inspecting and discussing small samples of either raw or exemplary or synthesized project data.  Further, very little of those discussions were  focused on classification
	(the addition of a labels to some unlabelled data). Rather, much time
	was spent in those meetings discussing {\em what to do next}; i.e. trying
	to determine what could be altered to better improve some business outcome.

@@

This paper assesses two methods  for ``peeking'': a model-based method called CROSSTREES and an instance-based method   called HOW. 
CROSSTREES were first developed by Lekkalapudi and Menzies to  explaining results from multi-objective optimizers~\cite{nva14}. This paper is the first
to apply CROSSTREES to defect prediction and contrast set learning. Also, that prior work evaluated
CROSSTREES against multi-objective optimizers and not   instance-based methods.

This paper uses three criteria to assess the value of HOW and CROSSTREES for
learning actionable analytics:
\be
\item
A planning system needs to be {\em effective}; i.e. if its recommendations
are applied then some statistically significant change should be observed.
To predict the number of defects in a data set before and after applying our changes,
we build a    prediction system (built by data mining; specifically: Random Forest). Note that this
predictor was built from some hold-out data (i.e. from  different data than that used
to build the predictor).
\item
Any  conclusion made to a business user must be understandable;
it must generate {\em succinct} changes.  
\item
Recommendations should be {\em stable}; i.e. they shouldn't widely vary due to minor changes in the data. Hence, in our experiments, we will add a little randomness to our analysis then report results across 20 repeated runs. 
\ee
We will find that
 {\em effectiveness} of CROSSTREES and HOW are similar, but   CROSSTREES wins on {\em succinctness} and {\em stability}.

@@

@@

\subsection{Results}
\input{tex/deltas_avg.tex}
The results for each data, for different planners, are shown in \fig{jur} and \fig{conf}. All
\subsection{Discussion}
\section{Threats to Validity}
\section{Conclusion}
\section*{Acknowledgements}
\bibliographystyle{plain}

>>>>

\title{Learning Useful Changes\\(to Reduce Runtimes and Software Defects)}
\numberofauthors{3} 
\author{
\alignauthor 
Rahul~Krishna,~Tim Menzies,~Xipeng~Shen \\
       \affaddr{Com. Sci., NC State, USA}\\
       {\{i.m.ralk,~tim.menzies,\\xipengshen\}@gmail.com}
\alignauthor
Naveen   Lekkalapudi\\
 \affaddr{Software Consultant } \\ 
       \affaddr{Washington D.C.}\\ 
       {navek91@gmail.com}
\alignauthor
Lucas Layman \\
       \affaddr{Fraunhofer CESE  } \\ 
       \affaddr{College Park, USA}\\ 
       {llayman@fc-md.umd.edu}
\setlength{\columnsep}{7mm}
}
\maketitle
\begin{abstract}
 As business users demand more insightful
 analytics, data scientists need to change
 their tools. Instead of merely predicting 
 some result, they also need tools that generate ``plans'';
 i.e. specific suggestions on  how to change values in order to
 improve on some predicted value.

@@

 This paper uses these learners to learn methods
 to reduce defects and decrease program runtime.
 For the test data of this paper, those improvements   reduce
 the expected values of defect counts and  runtimes to    
 72\%,75\%  (median) and 66\%,20\% (best case) of the initial values, respectively.
\end{abstract}
\section{Introduction}
We propose a novel {\em planning} approach called CROSSTREES for learning changes to a software system
such that its performance ``improvess'', according to some measure. For  casew
stuides, we apply CROSSTREES to   (1)~reducethe predicted number
of defects and (2)~reduce the runtimes of five system.

The approach discussed here is novel since most data miners used in software analytics
comment on ``what is'' and not ``what to do''. For example, a clustering
algorithm might find clumps of similar examples, but does not comment on the minimal
change(s) required to move from clump to clump.

Our approach is important for two reasons. Firstly, business users now demanding analytics tools that support a business-level interpretation of their data. At a panel on software analytics at ICSE’12, industrial practitioners lamented the state of the art in data mining and software engineering~\cite{menzies12a}. Panelists commented that ``prediction is all well and good, but what about decision making?''. That is, these panelists are more interested in the interpretations and follow-up that occurs after the mining, rather than just the mining itself. For example:
\bi
\item
Instead of just accepting {\em predictions} on how many software defects to expect, business users might now demand a {\em plan} to reduce the likelihood of those defects.
\item
Instead of just accepting {\em predictions} on the runtime time of their software, business users might now demand a {\em plan} to reduce that runtime. 
\ei
A second reason for the importance of our approach is, as shown below,
when asked how to change a project in order to achieve a result, it is surprisingly
difficult to use standard methods (e.g. clustering) to find those changes.
In the case study that motivated this paper, we how  standard data mining methods
can generate  seemingly
useful insights, but which are in fact completely ineffectual. On the other hand,
using CROSSTREES, we can propose changes that significantly reduce:
\bi
\item The  defects found  in Jureczko et al.'s    JAVA systems~\cite{jureczko10}.
\item The runtime of the  software    configured by  Seigmund et al.~\cite{sven12}.
\ei 
Since CROSSTREES is a somewhat novel algorithm, we present it in tutorial form.
The next section walks the reader through a sequence of approaches that start
with a standard clustering algorithm, and progresses on to CROSSTREES. The second
half of the paper then presents an extensive evaluation of CROSSTREES on 
the Jureczko  and Seigmund data sets. This is followed by notes on related work
and validity.

\section{From Clustering to  CROSSTREES}

In the summer of 2011 and 2012, one of us (Menzies) spent two months
	working on-site at Microsoft Redmond,
	observing data mining analysts.  In that study, he took special
	note about how Microsoft's data scientists
	discussed the results of their data mining sessions with  business users.

	One surprising observation was how  
	little time was spent by business users 
	inspecting  of the output of standard data miners. Prior to that visit,
	we had the mistaken impression that   decision trees,
	clustering algorithms, etc were useful ``off-the-shelf''; i.e    business
	users would inspect and understand the output of those tools.

Standard data mining tools are not necessarily the best tool for supporting that dialogue.
Menzies found that he had to do considerable work pre-processing data mining output
prior to the weekly briefing meetings for the business users. Initially,
that pre-processing was just clustering. This evolved into feature selection and finally
the a case-based reasoning tool called HOW.

	as compared to another process, which we call {\em peeking}.
	In {\em peeking}, analysts and users spend much time
	inspecting and discussing small samples of either raw or exemplary or synthesized project data.  Further, very little of those discussions were  focused on classification
	(the addition of a labels to some unlabelled data). Rather, much time
	was spent in those meetings discussing {\em what to do next}; i.e. trying
	to determine what could be altered to better improve some business outcome.

@@

This paper assesses two methods  for ``peeking'': a model-based method called DTREE and an instance-based method   called HOW. 
DTREE were first developed by Lekkalapudi and Menzies to  explaining results from multi-objective optimizers~\cite{nva14}. This paper is the first
to apply DTREE to defect prediction and contrast set learning. Also, that prior work evaluated
DTREE against multi-objective optimizers and not   instance-based methods.

This paper uses three criteria to assess the value of HOW and DTREE for
learning actionable analytics:
\be
\item
A planning system needs to be {\em effective}; i.e. if its recommendations
are applied then some statistically significant change should be observed.
To predict the number of defects in a data set before and after applying our changes,
we build a    prediction system (built by data mining; specifically: Random Forest). Note that this
predictor was built from some hold-out data (i.e. from  different data than that used
to build the predictor).
\item
Any  conclusion made to a business user must be understandable;
it must generate {\em succinct} changes.  
\item
Recommendations should be {\em stable}; i.e. they shouldn't widely vary due to minor changes in the data. Hence, in our experiments, we will add a little randomness to our analysis then report results across 20 repeated runs. 
\ee
We will find that
 {\em effectiveness} of DTREE and HOW are similar, but   DTREE wins on {\em succinctness} and {\em stability}.

@@

\begin{figure}[!t]
\includegraphics[width=0.9\linewidth]{_figs/BDBC.eps}
\caption{Feature Model}\label{fig:bdbc}
\end{figure}

@@

\subsection{Results}
\input{tex/deltas_avg.tex}
The results for each data, for different planners, are shown in \fig{jur} and \fig{conf}. All
\subsection{Discussion}
\section{Threats to Validity}
\input{tex/results_models.tex}
\section{Conclusion}
\section*{Acknowledgements}
\bibliographystyle{plain}
